Understanding the nanoscale structure of hexagonal phase lyotropic liquid crystal membranes

### 2017-12-12 Ben_Manuscripts/structure_paper/Draft.tex
Filling out text & some new figures

  The simulations best support a model built with 5 monomers per layer based on
  the measured pore-to-pore distances. To discern the composition of the monomer
  layers, addressing (\ref{point:monomernum}), we ran simulations of systems
  created with 4 - 8 monomers per layer. Systems were built in both the parallel
  displaced and sandwiched configurations and prepared according to
  the dry equilibration procedure. All systems are stable after 400 ns of
  simulation. Figure ~\ref{fig:p2p} shows the pore spacing for all systems
  tested. Systems built with 5 monomers in each layer equilibrate to a pore
  spacing that is most consistent with the experimental value of 4.12 nm derived
  from SAXS measurements (Figure~\ref{fig:SAXS}). The remainder of this
  discussion will focus on the analysis of systems built with 5 monomers per
  layer.

@@

  The peaks in the tilt angle distribution are consistent with the location of R-spots.
  \begin{itemize}
	\item The peaks of interest in Figures~\ref{fig:offset_tails}~and~\ref{fig:layered_tails}
	are located at $\pm$ 33 $\degree$ which is the same location where the highest intensity
	of spots are located on the simulated patterns
	\item We confirmed this conclusion by radially integrating the 2D WAXS pattern for q values
	between 1.57 and 1.4 (real space between 4 and 4.5 \AA) 
	\item We observe that distinct peaks appear c.a. 30 $\degree$, in close agreement with the
	previously measured angle distribution (~\ref{fig:offset_integration}~\ref{fig:layered_integration})
%	\item We integrated the raw experimental 2D WAXS data in the region bounding R-alkanes 
	\item We performed the same integration on the raw experimental data and found the angle
	at which R-spots reaches its highest intensity to be $\pm$ 37 $\degree$ which is a 
	reconcilable difference with our simulated results.  
  \end{itemize}

@@

  \begin{figure}
  \centering
  	\begin{subfigure}{\linewidth}
	\centering
		\begin{subfigure}{0.45\textwidth}
        		\centering
        		\includegraphics[width=\linewidth]{offset_tail_packing.png}
        		\caption{}~\label{fig:offset_tails}
		\end{subfigure}
		\begin{subfigure}{0.45\textwidth}
		\centering
	        	\includegraphics[width=\linewidth]{offset_angle_v_I.png}
		        \caption{}~\label{fig:offset_integration}
		\end{subfigure}
	\end{subfigure}
	\begin{subfigure}{\linewidth}
	\centering
		\begin{subfigure}{0.45\textwidth}
	        \centering
		        \includegraphics[width=\linewidth]{angles_traj_layered.png}
		        \caption{}~\label{fig:rz_layered}
		\end{subfigure}
		\begin{subfigure}{0.45\textwidth}
        	\centering
		        \includegraphics[width=\linewidth]{layered_angle_v_I.png}
		        \caption{}~\label{fig:layered_integration}
		\end{subfigure}
	\end{subfigure}
%MRS: 
  \caption{The distribution of angles w.r.t. the xy plane between alkane chain tail centroids and nearest
  neighbor centroids for equilibrated parallel displaced (a) and sandwiched (c) configurations. The
  same peaks are visible when the 2D simulated diffraction data is radially integrated in the R-alkanes region,
  (b) and (d) respectively.}~\label{fig:tail_packing}
%MRS2: not clear what the difference is between right and left side figures.
%BJC: That's good! One is angles measured between tail centroids and the other is radial integration of the simulated xrd patterns. I'll try make that more clear in the caption.
%MRS3: sorry, I meant to say not clear what the SOURCE of the data is in right vs. left.  Make sure colors and labels are consistent in final 
%MRS: not clear why some are angles with x axis, and some are angles w neighbors?  Shouldn't it be the same thing plotted in both graphs?
%BJC: I just need to get the labels right, they are the same thing technically
  \end{figure}

  The $z$-direction correlation functions show that layers in our model prefer
  to stack further apart than 3.7 \angstrom as suggested by experiment. We
  attempted equilibration with layers stacked 5.0 nm apart and to our surprise,
  we observed long-term stability of a qualitatively different configuration
  suggesting that we have found more than one metastable free energy basin,
  corroborating \ref{point:metastable}.
  \begin{itemize}
 	\item The diffraction pattern is different in the tail region
	\item The layer spacing is further apart
  \end{itemize}

  \begin{figure}[!ht]
        \centering
        \begin{subfigure}[b]{0.475\textwidth}
                \centering
                \includegraphics[width=\textwidth]{280K_tramp_close.png}
                \caption{}\label{fig:OPbasin}
        \end{subfigure}
        \begin{subfigure}[b]{0.475\textwidth}
                \centering
                \includegraphics[width=\textwidth]{340K_tramp_close_full.png}
                \caption{}\label{fig:DPbasin}
        \end{subfigure}
        \caption{From a qualitative standpoint, the ordered pore basin (a) is characterized by a
        hollow cylindrical pore while pores in the disorder pore basin (b) are characterized by a
        higher degree of radial disorder}\label{fig:basins}
%MRS3: see note on RDF.
  \end{figure}

  % INSERT XRD of disordered basin

  In order to address \ref{point:poredefinition} and to further understand the structural difference 
  between the ordered pore and disordered pore basins, we plotted the number of densities of
  heavy atoms in the head group and tail regions of the monomers in addition to the sodium ions.
  (See Supplemental Information for definition of head group and tail regions) 
  \begin{itemize}
	\item For the hydrophilic region, we used the carbon atoms making up the aromatic ring
	\item For the hydrophobic components we used all carbon atoms of the monomer tails
  \end{itemize}

@@

  We answer (\ref{point:water}) and further support (\ref{point:orientation}) by preparing parallel displaced and
  sandwiched configurations according to the wet equilibration procedure.
  \begin{itemize}
	\item We do not have an experimental measurement of water in the pores
	\item We tested a range of water concentrations from 0.5 to 5 percent % working on a 0.5 wt % sytstem now just to see
	\item Our lower bound represents a system with on average 2 water 
	molecules for each monomer layer.
	\item Figure ~\ref{fig:solvation} shows results for each configuration.
%	\item Initially, we decided the number of waters to put in each pore by
%	estimating the number of hydrogen bonds in which pore entities could participate.
%	\item In solution, each headgroup has a charge of -1
%	\item We estimate there to be at least 2 water molecules per layer based 
%	on various packing configurations and geometric constraints
%	\item 4 water molecules per layer translates to about 1.6 wt \%
  \end{itemize}

@@

  In all cases, water disrupts structuring of the model.
  \begin{itemize}
	\item The plots in Figure ~\ref{fig:solvation} are normalized 
	to have the same colorbar as the dry systems. 
	\item The intensity of the reflections decrease when water is 
	added to the system.
	\item In systems built with 5 weight percent water, R-$\pi$ and
	R-spots become nearly indistinguishable from R-alkanes.
  \end{itemize}

@@

  %BJC: old version of above figure v v v
  %\begin{figure}[ht]
  %\centering

  %\begin{subfigure}{0.3\linewidth}
  %      \centering
  %      \includegraphics[width=\linewidth]{offset_tail_packing.png}
  %      \caption{}~\label{fig:offset_tails}
  %\end{subfigure}
  %\begin{subfigure}{0.3\linewidth}
  %      \centering
  %      \includegraphics[width=\linewidth]{angles_traj_layered.png}
  %      \caption{}~\label{fig:layered_tails}
  %\end{subfigure}
  %\begin{subfigure}{0.3\linewidth}
  %      \centering
  %      \includegraphics[width=\linewidth]{integrated_WAXS_ring.png}
  %      \caption{}~\label{fig:rz_layered}
  %\end{subfigure}
  %\caption{The distribution of angles w.r.t. xy plane between alkane chain tail centroids and nearest
  %neighbor centroids for equilibrated parallel displaced (a) and sandwiched (b) configurations both show
  %distinct peaks at $\pm$ 33 $\degree$. (c) Integrated 2D WAXS data between $q_r$=1 and $q_r$=1.42 shows
  %distinct peaks at with maxima at $\pm$ 37 $\degree$}~\label{fig:tail_packing}
  %\end{figure}

%BJC: basin stuff that won't be included in this paper
%  The disordered basin shares little in common with the ordered basin but 
%  its long term stability suggests that it can exist under some conditions.  
%  We observed that Basin B is the dominant configuration at higher temperatures.
%  \begin{itemize}
%        \item We linearly ramped the temperature of a system in Basin A
%        from 280K to 340K (just below the experimental isotropic transition temperature) over 100 ns.
%        \item Visually, there is a distinct change in pore structure from one
%        characteristic of the OP Basin (Figure~\ref{fig:280K_pore}) to one characteristic of
%        the CP Basin (Figure~\ref{fig:340K_pore}).
%        \item The slope of all order parameters changes between 315K and 325K
%        (\Cref{fig:p2p_tramp,fig:thickness_tramp,fig:order_tramp}) indicating the
%        possibility of an abrupt change in system ordering.
%        \item Our 100 ns temperature ramp was likely too fast and caused the system
%        to suffer from hysteresis.
%  \end{itemize}

%  We can not immediately classify the OP Basin and the CP Basin as separate phases.
%  \begin{itemize}
%	\item To prove the existence of two phases we need evidence of a
%	a first order phase transition.
%	\item A first order phase transition can be denoted by a discontinuity
%        of some order parameter in response to an external condition such as
%	temperature.
%	\item We chose three easily measurable order parameters: the distance
%	between pores, the membrane thickness and the ratio of pore radius to
%	the uncertainty in pore radius.  % BJC: these may change
%        \item The pore radius is divided by its uncertainty as a way of quantifying
%        the degree to which monomers obstruct the pore region.
%  \end{itemize}

% In an attempt to mitigate hysteresis, we performed slow, stepwise temperature ramps
%  on a parallel displaced and a sandwiched configuration previously equilibrated at 300K.
%  \begin{itemize}
%        \item Every 200 ns, the temperature was raised 5K until we reached 345K
%	\item We performed the same procedure with a system equilibrated in the CP Basin
%	and used it as a benchmark for comparison. 
%  \end{itemize}
%
%  \begin{figure}[!ht]
%        \centering
%        \begin{subfigure}[b]{0.475\textwidth}
%                \centering
%                \includegraphics[width=\textwidth]{280K_tramp_close.png}
%                \caption{}\label{fig:280K_pore}
%        \end{subfigure}
%        \begin{subfigure}[b]{0.475\textwidth}
%                \centering
%                \includegraphics[width=\textwidth]{340K_tramp_close_full.png}
%                \caption{}\label{fig:340K_pore}
%        \end{subfigure}
%        \vskip\baselineskip
%        \begin{subfigure}[b]{0.325\textwidth}
%                \centering
%                \includegraphics[width=\textwidth]{p2p_tramp.png}
%                \caption{}\label{fig:p2p_tramp}
%        \end{subfigure}
%        \begin{subfigure}[b]{0.325\textwidth}
%                \centering
%                \includegraphics[width=\textwidth]{thickness_tramp.png}
%
%                \caption{}\label{fig:thickness_tramp}
%        \end{subfigure}
%        \begin{subfigure}[b]{0.325\textwidth}
%                \centering
%                \includegraphics[width=\textwidth]{order_tramp.png}
%                \caption{}\label{fig:order_tramp}
%        \end{subfigure}
%        \caption{(a) The open pore structure exhibited by a structure equilibrated
%        at 280K is characteristic of the OP Basin. (b) The closed pore structure with
%        a high degree of radial disorder exhibited when the structure in (a) is
%        heated to 340K is characteristic of the CP Basin. (c) A plot of distance between pores
%        vs. temperature changes slope near 325K. (d) A plot of membrane thickness vs.
%        temperature changes slope near 325K. (e) The plot of the ratio of pore radius to
%        its uncertainty changes slope near 315K.}\label{fig:tramp}
%  \end{figure}

%  The CP and OP basins are two configurationally metastable basins.
%  \begin{itemize}
%        \item There is litle change in CP basin properties during the 
%        temperature ramp.
%	\item We observed smooth changes in order parameters as temperature
%        of the OP Basin system was increased implying that we cannot claim the
%	existence of two phases (Figure~\ref{fig:phase_transition}).
%	\item Qualitatively, the pore structure of the OP basin system becomes
%        comparable to one characteristic of the CP basin as temperature is raised. (\Cref{fig:BasinA_280K_pore,fig:BasinB_340K_pore})
%	\item The OP basin system does not converge to the same order parameter
%	values as the CP basin, however it is trending towards Basin B values. (\Cref{fig:p2p_step,fig:thickness_step,fig:order_step})
%	\item To resolve the quanitative discrepancy, we would need a slower 
%	temperature ramp
%	\item Since there are no abrupt changes in any order parameter along the 
%	trajectory, we can conclude that the two basins are not separate phases
%	\item The OP basin is the closest match to what is seen experimentally
%	\item The CP basin is likely an intermediate between the Col\textsubscript{h} 
%	phase and isotropic phase
%	\item The CP basin is present in our simulations at lower temperatures 
%        %MRS: lower temperatures than experiment.  Though nobody has really done the experiments.  
%        %MRS: can we conclude anything from some of the in-situ temperature measurements done by Xunda?  We talked about them, but I don't know they are referenced here.
%	%BJC: Not with what we have because it's in-situ SAXS data which only shows the pore spacing
%	than experiment because our model lacks sufficient $\pi$-$\pi$ iteractions necessary to 
%	stabilize the system into the OP basin. 
%  \end{itemize} 
%
%  \begin{figure}[!ht]
%        \centering
%	% BJC: I'll get actual pictures of the system here. I'm not sure how 
%	% necessary this figure is though. It could go in the supplemental 
%	% information and I can reference the pictures in the previous figure
%	% since they show basically the same idea : Ordered vs. disordered pore
%	% Alternatively, I could show two diffraction patterns here from the 
%	% beginning and end temperature 
%        \begin{subfigure}[b]{0.475\textwidth}
%                \centering
%                \includegraphics[width=\textwidth]{280K_tramp_close.png}
%                \caption{}\label{fig:BasinA_280K_pore}
%        \end{subfigure}
%        \begin{subfigure}[b]{0.475\textwidth}
%                \centering
%                \includegraphics[width=\textwidth]{340K_tramp_close_full.png}
%                \caption{}\label{fig:BasinB_340K_pore}
%        \end{subfigure}
%	\vskip\baselineskip
%        \begin{subfigure}[b]{0.325\textwidth}
%                \centering
%                \includegraphics[width=\textwidth]{p2p_layered.png}
%                \caption{}\label{fig:p2p_step}
%        \end{subfigure}
%        \begin{subfigure}[b]{0.325\textwidth}
%                \centering
%                \includegraphics[width=\textwidth]{thickness_layered.png}
%
%                \caption{}\label{fig:thickness_step}
%        \end{subfigure}
%        \begin{subfigure}[b]{0.325\textwidth}
%                \centering
%                \includegraphics[width=\textwidth]{order_layered.png}
%                \caption{}\label{fig:order_step}
%        \end{subfigure}
%
%	\caption{In all cases, blue lines represent the measured value of
%	the order parameter, black lines are average values calculated from
%	equilibrated Basin B systems at each temperature, green shaded regions
%	represent the standard deviation of each of the black line values, and 
%	red dashed lines show where the temperature is bumped to the next level.
%	(a) At 280K, the system is in a configuration reminiscent of
%	Basin A. (b) At 335K, the system resembles a Basin B configuration. (c) The pore
%	spacing of Basin A decreases with temperature approaching the value 
%	exhibited by Basin B. (d) The thickness of Basin A increases smoothly with 
%	temperature but is far from the Basin B value. Longer equilibrations at 
%	each temperature are needed to allow the system to fully expand. 
%        (e) The ratio of pore radius to uncertainty for Basin A changes smoothly with temperature,
%	converging to a value below that exhibited by Basin B.}\label{fig:phase_transition}
%  \end{figure}

@@

  We use the equilibrated parallel displaced system to calculate ionic 
  conductivity since its structure is the closest match to experiment.
  The model gives reasonable estimates of ionic conductivity when compared to 
  experiment.
  \begin{itemize}
  	\item Calculated values of ionic conductivity obtained using the Nernst 
	Einstein relation and Collective Diffusion model are compared in 
	Figure~\ref{fig:conductivity}.
	\item The two methods agree with each other within error, although the 
	uncertainty obtained using the Collective Diffusion model is much higher.
	\item Much longer simulations are needed to lower the uncertainty, however it
	is not feasible to do so with a large system.  
	\item For this reason we will likely only use the Nernst Einstein relation
	in future calculations of this type. 
  \end{itemize}

  The calculated values of ionic conductivity are higher than experiment by an
  order of magnitude. 
  \begin{itemize}
	\item One can justify the reason for this result by considering the 
	real system studied experimentally
	\item The ionic conductivity measurement to which we are comparing was done
	on a \SI{80}{\micro\metre} thick film, nearly 10,000 times thicker than 
        our simulated system. 
	\item The thick film likely has defects leading to non-contiguous pores and
	imperfect alignment.
	\item The 2D SAXS pattern shows the small degree of tortuosity present
	in the system (~\ref{fig:2DSAXS})  % BJC: insert 2D SAXS data -- maybe azimuthal distribution
	\item It has been shown that there is a large dependence of Ionic conductivity
	on the alignment of the pores
	\item The ionic conductivity of an unaligned film is 85 times lower than that
	of a nearly aligned film referenced here  % BJC: reproduce figure from 2014
	\item It is not unreasonable that a thin, perfectly aligned film would have 
	a value of ionic conductivity in agreement with our model
  \end{itemize}

  \begin{figure}
  \centering
  \includegraphics[width=0.5\linewidth]{2D-SAXS_cropped.png}
  % BJC: I will add axes with q values if this ends up in the final draft
  % BJC: I'll also see what I can do about all the white speckles
%MRS2: I'm not sure what the point of this figure is?
%BJC: I put it here at some point in case the need arises. It's mainly to show
% that the pores in the real system are somewhat tortuous, in place of showing
% the Azimuthal distribution which is just an integration of this data. I thought
% it'd be clearer that way since but maybe it's not?
%MRS3: state more clearly in the caption why you are showing it. i.e. ``this data shows that pores in the system are somewhat tortuous'', then explain how the figure shows that.
  \caption{The experimental two dimensional SAXS pattern exhibits reflections
  resulting from highly aligned pore regions. A perfectly aligned system 
  would exhibit sharp dots at the same locations of the refelctions shown. 
  An isotropically aligned system the reflections would appear as 
  rings centered about the origin}~\label{fig:2DSAXS}
  \end{figure}

@@

%  The CP basin has a higher ionic conductivity than the OP basin.
%  \begin{itemize}
%	\item We hypothesize that conductivity is enhanced in Basin B due to a 
%	higher sodium ion diffusivity.
%	\item Transport of sodium is likely facilitated by the homogeneity of Basin B.
%	Sodium ions have less nearby sites to move to in Basin A.
%	\item There is currently no experimental evidence of this trend. Maybe Xunda will find something
%	\item In both cases, our calculated values for Basin A are higher than the 
%	experimental values, as expected. 
%	\item Some of the discrepancy is likely a result of using an imperfect forcefield. 
%	\item However, the real system, although mostly aligned and straight, has a 
%	distribution of azimuthal angles, meaning that the pores have a degree of 
%	tortuosity which lowers the effective ionic conductivity of the bulk membrane. 
%	\item The ordering from isotropic to mostly aligned mesophases showed an 85 
%	fold increase in ionic conductivity. We would expect additional gains in a 
%	perfectly aligned system.
%  \end{itemize}

%BJC: vvv replaced by bar plot above
%  \begin{table}[h]
%  \centering
%  \begin{tabular}{ccc}
%  \toprule
%  \multicolumn{3}{c}{Calculated Ionic Conductivity \si{\siemens\per\meter}} \\
%  \hline
%  Method & Basin A & Basin B \\
%  \midrule
%  Nernst Einstein & \num{1.23e-4} (0.01) & \num{1.76e-4} (0.02) \\
%  Collective Diffusion & \num{1.40e-4} (0.32) & \num{4.6e-4}(2.4) \\
%  Experiment & \num{1.33e-5} (0.10) & -- \\
%  \bottomrule
%  \end{tabular}
%  \caption{Calculated ionic conductivity using Nernst-Einsten and Collective Diffusion 
%  agree within error. Both methods give calculated values of ionic conductivity which
%  are an order of magnitude higher than experimental values~\label{table:conductivity}}.
%  \end{table}

  %MRS: the next sections maybe should be supporting?
  %MRS: you say ``the distance decreases by 1 A'' but is that true
  %over all of the different structures?
  %BJC: limiting the discussion to the OP basin in the offset configuration 
  %MRS: Maybe show the difference before and after crosslinking in X-ray, to show that you can't tell?
  %MRS: you don't otherwise discuss clearly what effect crosslinking would have. 
  \subsection*{Implementation of the crosslinking algorithm}

@@

%  \begin{figure}
%	\centering
%	\begin{subfigure}{0.31\textwidth}
%		\centering
%		\includegraphics[width=\textwidth]{p2p_diagram.PNG}
%		\caption{}\label{fig:p2p_diagram}
%	\end{subfigure}
%		\begin{subfigure}{0.31\textwidth}
%		\centering
%		\includegraphics[width=\textwidth]{no_xlink_p2p.png}
%		\caption{}\label{fig:no_xlink_p2p}
%	\end{subfigure}
%		\begin{subfigure}{0.31\textwidth}
%		\centering
%		\includegraphics[width=\textwidth]{xlink_p2p.png}
%		\caption{}\label{fig:xlink_p2p}
%	\end{subfigure}
%	\caption{(a) The legends of the plots in (b) and (c) refer to the numbers shown.
%	Each numbered circle represents a pore. Distances are measured along each of the 
%	lines shown in addition to the distance from pore 1 to pore 4. (b) The positions
%	of individual pores fluctuate in an uncrosslinked system. (c) The positions of
%	individual pores in the crosslinked system are stable relative to the uncrosslinked
%	system}\label{fig:xlink}
%  \end{figure}

@@

  We have used a detailed molecular model of the Col\textsubscript{h} phase formed by NA-GA3C11
  in order to study the nanoscopic structure.
  \begin{itemize}
  	\item While there have been efforts to model formation of various liquid crystalline 
	phases with molecular dynamics, to our knowledge there have been no studies which 
	attempt to examine their structure with the same level of detail presented here.
	\item Evidence strongly supports that layers are composed of 5 monomers
        \item We have confirmed that monomers stay partitioned in layers.
	\item We have explored the affect of two different $\pi$-$\pi$ stacking modes on the equilibrated
	membrane strucure. 
	\item Simulated diffration patterns generated from MD trajectories suggest that
	the parallel-displaced configuration produces a structure with the closest match to experiment.
%MRS3: water is not needed to create well-defined pore structures?  I'm not sure ``maintain'' is the right word, and ``membrane structure'' may be too vague.
	\item Finally, water is not needed to maintain membrane structure our data 
	shows that it actually disorders the pore
	\item Now that we have a good idea of what the membrane structure should look like, we will
	evaluate transport of various solutes within the system. 
         %MRS2: I'd like to see a bit more information about ``pore size'', and the RDF's of the constituents.  What FITS through a pore is another paper.
        \item We will apply the knowledge gained from this study in order to 
        suggest improvements to the existing system as well as to evaluate new
	unsynthesized LLC systems.
%	\item Even though our model only answers these questions for a system created by 
%	NA-GA3C11, it can be adapted to other study systems formed by other LCs with 
%	little extra effort. 
  \end{itemize}

>>>>

  The simulations best support a model built with 5 monomers per layer based on
  the measured pore-to-pore distances. To discern the composition of the
  monomer layers, addressing (\ref{point:monomernum}), we ran simulations of
  systems created with 4 - 8 monomers per layer. Systems were built in both the
  parallel displaced and sandwiched configurations and prepared according to the
  dry equilibration procedure. All systems are stable after 400 ns of simulation.
  In a sense, all systems are at least metastable, addressing
  \ref{point:metastable}, however not all will make physical sense or fit the
  experimental profile that we are looking to match. Figure ~\ref{fig:p2p}
  shows the pore spacing for all systems tested. Systems built with 5 monomers in
  each layer equilibrate to a pore spacing that is most consistent with the
  experimental value of 4.12 nm derived from SAXS measurements
  (Figure~\ref{fig:SAXS}). The remainder of this discussion will focus on the
  analysis of systems built with 5 monomers per layer.

@@

  The peaks in the tilt angle distribution are consistent with the location of
  R-spots. The peaks of interest in Figures \ref{fig:offset_tails} and
  \ref{fig:layered_tails} are located at $\pm$ 33 $\degree$ which is the same
  location where the highest intensity of spots are located on the simulated
  patterns. We confirmed this conclusion by radially integrating the 2D WAXS
  pattern for q values between 1.57 and 1.4 (real space between 4 and 4.5 \AA). We
  observe that distinct peaks appear ca. 30 $\degree$, in close agreement with
  the previously measured angle distribution
  (~\ref{fig:offset_integration}~\ref{fig:layered_integration}). We performed the
  same integration on the raw experimental data and found the angle at which
  R-spots reaches its highest intensity to be $\pm$ 37 $\degree$ which is a
  reconcilable difference with our simulated results.

@@

  \begin{figure}
  \centering
  	\begin{subfigure}{\linewidth}
	\centering
		\begin{subfigure}{0.45\textwidth}
        		\centering
        		\includegraphics[width=\linewidth]{offset_tail_packing.png}
        		\caption{}~\label{fig:offset_tails}
		\end{subfigure}
		\begin{subfigure}{0.45\textwidth}
		\centering
	        	\includegraphics[width=\linewidth]{offset_angle_v_I.png}
		        \caption{}~\label{fig:offset_integration}
		\end{subfigure}
	\end{subfigure}
	\begin{subfigure}{\linewidth}
	\centering
		\begin{subfigure}{0.45\textwidth}
	        \centering
		        \includegraphics[width=\linewidth]{angles_traj_layered.png}
		        \caption{}~\label{fig:rz_layered}
		\end{subfigure}
		\begin{subfigure}{0.45\textwidth}
        	\centering
		        \includegraphics[width=\linewidth]{layered_angle_v_I.png}
		        \caption{}~\label{fig:layered_integration}
		\end{subfigure}
	\end{subfigure}
%MRS: 
  \caption{The distribution of angles w.r.t. the xy plane between alkane chain tail centroids and nearest
  neighbor centroids for equilibrated parallel displaced (a) and sandwiched (c) configurations. The
  same peaks are visible when the 2D simulated diffraction data is radially integrated in the R-alkanes region,
  (b) and (d) respectively.}~\label{fig:tail_packing}
  \end{figure}

%  The $z$-direction correlation functions show that layers in our model prefer
%  to stack further apart than 3.7 \angstrom as suggested by experiment.
  When systems are built with layers stacked 5.0 \angstrom apart then equilibrated, 
  we observe long-term stability of a qualitatively different configuration
  suggesting that we have found another metastable free energy basin,
  further corroborating \ref{point:metastable}. We studied this type of system in
  both the parallel displaced and sandwiched configurations.

  Structural properties are different when layers are initially spaced 5 \AA apart.
  \begin{itemize}
	\item In both configurations we observe a decrease in pore spacing along with an increase in the equilibrated distance between layers.
	\item The simulated X-ray diffraction patterns differ particularly with reference to R-spots.
	\item R-helix is still faintly visible in the parallel displaced and absent in the sandwiched simulated diffraction pattern implying that head groups maintain their initial ordering to a degree.
	\item In both cases, R-spots is markedly different.
	\item When layers stack too far apart, they do not exhibit hexagonal packing
	\item The intensity within R-alkanes of the parallel displaced configuration is nearly uniform with slightly more concentrated intensity at the top and bottom.
	\item The sandwiched configuration possesses higher intensity regions at the top and bottom of R-alkanes as well as along the equator with high intensity near q$_z$ = 0.
  \end{itemize}

  \begin{figure}
        \centering
        \begin{subfigure}{0.45\linewidth}
                \centering
                \includegraphics[width=\linewidth]{offset_disordered_rzplot.png}
                \caption{}~\label{fig:offset_disordered_xrd}
        \end{subfigure}%
        \begin{subfigure}{0.45\linewidth}
                \centering
                \includegraphics[width=\linewidth]{layered_disordered_rzplot.png}
                \caption{}~\label{fig:layered_disordered_xrd}
        \end{subfigure}
        \begin{subfigure}{0.45\linewidth}
                \centering
                \includegraphics[width=\linewidth]{dbwl.png}
                \caption{}~\label{fig:dbwl_disordered}
        \end{subfigure}%
        \begin{subfigure}{0.45\linewidth}
                \centering
                \includegraphics[width=\linewidth]{p2p2.png}
                \caption{}~\label{fig:p2p_disordered}
        \end{subfigure}
	\caption{In comparison to systems built with 3.7 \AA initial layer spacing,  
                the simulated X-ray diffraction patterns of the parrallel displaced (a) and 
 		sandwiched (b) configurations are different when systems are built with 
 		a 5 \AA initial layer spacing, most notably in the region bounded by R-alkanes.
      		When layers are stacked further apart, the distance between layers increases (c)
                and the pore spacing decreases (d).}
  \end{figure}

  In order to address \ref{point:poredefinition}, we plotted the number of
  densities of heavy atoms in the head group and tail regions of the monomers in
  addition to the sodium ions. (See Supplemental Information for definition of
  head group and tail regions). For the head group region, we used the carbon
  atoms making up the aromatic ring For the tail regions we used only carbon
  atoms of the monomer tails

@@

  % BJC: necessary to show layered configurations at this point?
  We answered (\ref{point:water}) and further support (\ref{point:orientation})
  by preparing parallel displaced and sandwiched configurations according to the
  wet equilibration procedure. There is no experimental measurement of trace
  water concentration in the pores. We tested a range of water concentrations
  from 0.5 to 5 percent. Our lower bound models a system with on average 2 water
  molecules for each monomer layer. Figure ~\ref{fig:solvation} shows the
  simulated diffraction patters resulting from each configuration.

@@

  In all cases, water disrupts structuring of the model. The plots in Figure
  ~\ref{fig:solvation} are normalized to have the same colorbar as the dry
  systems. The intensity of the reflections decrease when water is added to the
  system. In systems built with 5 weight percent water, R-$\pi$ and R-spots
  become nearly indistinguishable from R-alkanes.

@@

@@

  We use the equilibrated parallel displaced system to calculate ionic
  conductivity since its structure is the closest match to experiment. The model
  gives reasonable estimates of ionic conductivity when compared to experiment.
  Calculated values of ionic conductivity obtained using the Nernst Einstein
  relation and Collective Diffusion model are compared in
  Figure~\ref{fig:conductivity}. The two methods agree with each other within
  error, although the uncertainty obtained using the Collective Diffusion model
  is much higher. Much longer simulations are needed to lower the uncertainty,
  however it is not feasible to do so with a large system. We will only use the
  Nernst Einstein relation in future calculations of this type.

  The calculated values of ionic conductivity are higher than experiment by an
  order of magnitude. One can justify the reason for this result by considering
  the real system studied experimentally. The ionic conductivity measurement to
  which we are comparing was done on a \SI{80}{\micro\metre} thick film, nearly
  10,000 times thicker than our simulated system. The thick film likely has
  defects leading to non-contiguous pores and imperfect alignment. The 2D SAXS
  pattern shows the small degree of tortuosity present in the system
  (~\ref{fig:2DSAXS}). It has been shown that there is a large dependence of
  ionic conductivity on the alignment of the pores. The ionic conductivity of an
  unaligned film is ca. 85 times lower than that of a nearly aligned film
  referenced here. We hypothesize that a thin, perfectly aligned film would have
  a value of ionic conductivity in agreement with our model

@@

  \begin{figure}
  \centering
  \includegraphics[width=0.5\linewidth]{2D-SAXS_cropped.png}
  \caption{Experiments confirm that the pores have a small degree of tortuosity. 
  The experimental two dimensional SAXS pattern exhibits reflections
  resulting from highly aligned pore regions. A perfectly aligned system 
  would exhibit sharp dots at the same locations of the refelctions shown. 
  An isotropically aligned system the reflections would appear as 
  rings centered about the origin}~\label{fig:2DSAXS}
  \end{figure}

  \subsection*{Implementation of the crosslinking algorithm}

@@

@@

  % add stuff about pore structure and 'disordered' basin once there are concrete results 
  We have used a detailed molecular model of the Col\textsubscript{h} phase
  formed by NA-GA3C11 in order to study its nanoscopic structure. While there
  have been efforts to model formation of various liquid crystalline phases with
  molecular dynamics, to our knowledge there have been no studies which attempt
  to examine their structure with the same level of detail presented here.
  Evidence strongly supports that layers are composed of 5 monomers. We have
  confirmed that monomers stay partitioned into layers. We have explored the
  affect of two different $\pi$-$\pi$ stacking modes on the equilibrated membrane
  strucure. Simulated diffration patterns generated from MD trajectories suggest
  that the parallel-displaced configuration produces a structure with the closest
  match to experiment. Finally, water is not needed to create well-definied pore
  structures. Now that we have a good idea of what the membrane structure should
  look like, we will evaluate transport of various solutes within the system. We
  will apply the knowledge gained from this study in order to suggest
  improvements to the existing system as well as to evaluate new unsynthesized
  LLC systems.
